\documentclass[10pt,a4paper]{article}

\usepackage[top=1.25cm,bottom=1.25cm,left=1.55cm,right=1.55cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage{tabularx}

\setmainfont{texgyreheros-regular.otf}[
  BoldFont=texgyreheros-bold.otf,
  ItalicFont=texgyreheros-italic.otf,
  BoldItalicFont=texgyreheros-bolditalic.otf
]
\setsansfont{texgyreheros-regular.otf}[
  BoldFont=texgyreheros-bold.otf,
  ItalicFont=texgyreheros-italic.otf,
  BoldItalicFont=texgyreheros-bolditalic.otf
]


\renewcommand{\familydefault}{\sfdefault}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6.2pt}

\definecolor{ink}{HTML}{202124}
\definecolor{muted}{HTML}{5F6368}
\definecolor{accent}{HTML}{2F6F63}
\definecolor{line}{HTML}{D8E2DF}

\hypersetup{
  pdftitle={Cover Letter - Valeria Kierbel},
  pdfauthor={Valeria Kierbel},
  colorlinks=true,
  urlcolor=accent
}

\newcommand{\header}{
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    {\fontsize{24}{27}\selectfont\bfseries\color{ink}Valeria Kierbel} &
    {\small\color{muted}\href{mailto:valereea@gmail.com}{valereea@gmail.com}}\\[-1pt]
    {\small\color{accent}\textbf{CS Supervisor Application}} & {}
  \end{tabularx}
  \vspace{7pt}
  \noindent\makebox[\textwidth][l]{%
    {\color{accent}\rule{0.18\textwidth}{1.2pt}}%
    {\color{line}\rule{0.82\textwidth}{1.2pt}}%
  }
  \vspace{9pt}
}

\begin{document}
\color{ink}
\fontsize{10.15}{13.25}\selectfont

\header

{\large\bfseries\color{ink}Customer Service Supervisor Cover Letter}

\vspace{4pt}

Dear Jerry,

I am writing to express my interest in the Customer Service Supervisor role because I genuinely enjoy supporting people and helping teams feel confident in what they do. I am motivated by opportunities to help colleagues grow, to contribute more directly to the department, and to take on additional responsibility in a role where I can make a broader impact. For me, this position is appealing not only because it involves leadership and service quality, but because it creates the chance to support people in a practical and encouraging way while helping the team deliver a consistent customer experience.

Although I have not been an agent for very long, I am a quick learner, highly self-motivated and always keen to lead by example. In my current role at Uniqlo, I have already had the opportunity to contribute beyond my daily duties: I was awarded Agent of the Month, I work confidently with VOC and TCD, I have presented information during Team Talks, trained both individuals and groups of agents, checked dispositions and order numbers, and supported the team with translation tasks. These experiences have helped me understand the needs of agents more clearly and have strengthened my confidence in supporting others.

My previous roles show that I can support consistency and strong performance. As a Restaurant Manager, during my eight years as an Associate Team Leader at Whole Foods, and through my experience as a teacher, I learned how to create a positive environment where people feel included, trusted and part of the team.

\textbf{Current operational challenge: Case Classification}

One operational challenge in a customer service environment is helping agents become confident and accurate when classifying cases. With my previous leadership experience, I would bring an additional coaching-oriented approach to this area alongside QA and Training. I value peer support, practical guidance and knowledge sharing, and I would aim to help agents understand the reasoning behind classifications rather than simply correcting mistakes. In my experience, that kind of support helps people improve faster and makes them more confident in their decisions.

I am also comfortable taking ownership of escalations and complex cases. As a Duty Manager, I was often responsible for the whole shop and had to deal with challenging situations where calm judgement and clear decision-making were essential. That experience has made me confident de-escalating situations, listening carefully, and looking for solutions that work for both the customer and the business while staying within policy.

I understand that in EU Customer Service, agents need clear guidance so that SOPs, GDPR, consumer rights regulations and brand values are applied correctly. In my previous roles I kept processes up to date, developed systems to track daily tasks and product knowledge, and helped the team understand what was expected of them.

As an Associate Team Leader, I learned the importance of being a second pair of eyes, stepping up when needed and helping the Market Leader keep things running smoothly. I have carried out one-to-one reviews, monitored performance and used constructive feedback, coaching and leading by example to help people grow.

Thank you for considering my application. I would welcome the opportunity to discuss how my experience in team leadership, operations, coaching and customer service could support the team and help me succeed as a Customer Service Supervisor.

\vspace{4pt}

Kind regards,

\textbf{Valeria Kierbel}

\end{document}
