\documentclass[11pt,a4paper]{article}

\usepackage[top=1.25cm,bottom=1.15cm,left=1.15cm,right=1.15cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{microtype}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{pagecolor}

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=2pt}

\definecolor{heading}{RGB}{25,25,25}
\definecolor{timelineblue}{RGB}{30,58,95}
\definecolor{timelinegray}{RGB}{80,80,80}

\definecolor{pagebg}{RGB}{241,241,244}
\definecolor{cardbg}{RGB}{255,255,255}
\pagecolor{pagebg}

\titleformat{\section}{\large\bfseries\color{heading}}{}{0pt}{}[\vspace{-4pt}\hrule\vspace{4pt}]

\usepackage{tikz}
\usetikzlibrary{positioning}

\newcommand{\projectcard}[4]{
\noindent
\begin{tikzpicture}
\node[
    text width=0.96\textwidth,
    fill=cardbg,
    draw=timelinegray!25,
    rounded corners=3pt,
    inner sep=8pt,
    align=left
] (box) {
\begin{tabularx}{0.96\textwidth}{@{}p{0.9cm}@{\hspace{0.35cm}}X@{}}
{\Huge\color{timelineblue}#1} &
\begin{minipage}[t]{\linewidth}
{\large\textbf{#2}}\\[4pt]
{\footnotesize #3}
\end{minipage}
\end{tabularx}
};

\node[
    anchor=south east,
    fill=gray!8,
    draw=timelinegray!20,
    rounded corners=2pt,
    inner xsep=5pt,
    inner ysep=2pt
] at ([xshift=-6pt,yshift=6pt]box.south east) {
    {\tiny #4}
};

\end{tikzpicture}
\vspace{6pt}
}

\begin{document}

\begin{tikzpicture}[remember picture,overlay]
\node[
    anchor=south,
    yshift=0.35cm,
    text width=18.2cm,
    fill=cardbg,
    draw=timelineblue!35,
    rounded corners=5pt,
    inner sep=8pt
] at (current page.south) {
{\scriptsize
{\small\bfseries\color{timelineblue}
\faCogs\ SKILLS
}

{\color{timelineblue!40}\rule{\linewidth}{0.4pt}}

\vspace{3pt}
\begin{tabularx}{18.0cm}{@{}X X X X X@{}}
\textbf{\color{timelineblue}Android} &
\textbf{\color{timelineblue}MDM} &
\textbf{\color{timelineblue}Architecture} &
\textbf{\color{timelineblue}Delivery} &
\textbf{\color{timelineblue}Secure Infra} \\[3pt]

Kotlin / Android SDK &
Android Enterprise &
MVVM &
Gradle &
MOD Environments \\

Device Owner &
Device Policy Manager &
Clean Architecture &
CI/CD &
Active Directory \\

Kiosk Mode &
Secure APK Updates &
Coroutines / Flow &
Automated Testing &
Kerberos / SPNEGO \\

REST APIs &
Secure Mobile Apps &
Offline-first Systems &
Python / PowerShell &
SMB / GPO / JML \\
\end{tabularx}
}
};
\end{tikzpicture}
\begin{tabularx}{\textwidth}{X r}
    {\LARGE \textbf{Daniele Della Cioppa}} &
    \href{https://github.com/danieledellacioppa}{\LARGE \faGithub\ GitHub} \\
    {\large Android Software Engineer --- Secure MDM \& Endpoint Control} &
    \href{https://www.linkedin.com/in/daniele-della-cioppa-41b062115/}{\LARGE \faLinkedin\ LinkedIn} \\
    London, UK & \\
\end{tabularx}

\smallskip
\smallskip
\smallskip
\smallskip

\footnotesize{
Android Software Engineer focused on Kotlin, secure Android mobile applications, MDM and endpoint control for Ministry of Defence (MOD) environments. I build Android Device Owner and Android Enterprise workflows using Device Policy Manager, kiosk lockdown, controlled APK update delivery, REST API integration, Gradle builds and policy-driven device behaviour.

I also bring identity and infrastructure automation experience across Active Directory, Kerberos/SPNEGO, SMB storage, Group Policy, Folder Redirection and Joiner/Mover/Leaver (JML) workflows using Python and PowerShell, supporting secure mobile estate integration with enterprise Windows and MOD networks.

}


\section*{Work Experience}

\renewcommand{\arraystretch}{1.12}
\begin{tabularx}{\textwidth}{>{\raggedleft\arraybackslash}p{2.4cm} !{\color{timelinegray}\vrule width 0.8pt} >{\raggedright\arraybackslash}X}
\textbf{\color{timelineblue}\shortstack[r]{2025--2026\\Current}} &
\textbf{Software Developer --- Akhter Computers}\\
& {\small\color{timelinegray}\textbf{Secure Android, MDM and Infrastructure Automation}}
\begin{itemize}
    \item Built secure MOD-environment prototypes combining endpoint-control requirements with Active Directory onboarding, Kerberos/SPNEGO authentication, backend token services and protected file access workflows.
    \item Implemented a Windows Single Sign-On flow where a domain user obtains Kerberos tickets, negotiates with a Python FastAPI identity service, receives an RS256 JWT, and accesses backend services through JWKS-validated trust.
    \item Validated Samba Active Directory and Windows Server 2022 lab environments covering AD, DNS, Kerberos, domain logon, Windows 11 Pro domain join behaviour, SPNs, keytabs and GSSAPI service validation.
    \item Moved the project direction toward enterprise-native AD/SMB/GPO automation: central user storage through SMB, Folder Redirection through Group Policy, JML workflows and Python/PowerShell orchestration.
    \item Built a Pairing-Based Domain Onboarding Tool for guided server/client onboarding, including pairing flow, client DNS configuration, domain join workflow and validation-oriented state-machine planning.
    \item Created deployment workflows for Python services using Debian packages, virtual environments, systemd services, environment files, hardened runtime configuration and KVM-backed reproducible lab testing.
\end{itemize} \\[3pt]

\textbf{\color{timelineblue}2024--2025} &
\textbf{Android System Developer --- Distributed Device Systems}\\
& {\footnotesize\color{timelinegray}
\begin{itemize}
    \item Developed Kotlin Android features for distributed digital-signage and device-synchronisation systems using a local-first architecture for secure or limited-connectivity environments.
    \item Integrated Android clients with REST APIs and Linux-backed services for content delivery, command/status reporting, update orchestration and remote operational tooling.
    \item Structured Android components around MVVM and Clean Architecture boundaries so UI, device orchestration, API, persistence and policy logic remained maintainable and testable.
    \item Used Kotlin coroutines and Flow for asynchronous device state, background sync, network calls, live status updates and resilience during intermittent connectivity.
\end{itemize}} \\[2pt]

\textbf{\color{timelineblue}2023--2024} &
\textbf{Android System Developer --- Remote MDM \& Update Infrastructure}\\
& {\footnotesize\color{timelinegray}
\begin{itemize}
    \item Developed Android MDM and endpoint-control infrastructure for managed devices, including Device Owner provisioning, Android Enterprise policy flows, Device Policy Manager integrations and kiosk mode lockdown.
    \item Built Kotlin secure Android mobile application components for remote management, device status reporting, controlled command handling and local policy enforcement.
    \item Implemented secure APK delivery and update workflows with signature/hash verification, controlled rollout behaviour and administrator-authorised privileged actions.
    \item Worked with Gradle-based Android builds, CI/CD release packaging and automated validation workflows across Android clients, Linux-backed services and operational tooling.
\end{itemize}} \\[2pt]

\textbf{\color{timelineblue}2021--2023} &
\textbf{Software Development Apprenticeship}\\
& {\scriptsize\color{timelinegray}
\begin{itemize}
    \item Contributed to IoT and Android projects involving telemetry, REST/gateway communication, PostgreSQL-backed monitoring, field diagnostics and automated testing.
    \item Built a foundation in systems development, debugging and customer-facing operational support.
\end{itemize}}
\end{tabularx}

\clearpage
\section*{Main Projects}

\projectcard
{\faMobile}
{Android MDM, Device Owner \& Kiosk Mode}
{Developed secure Android endpoint-control features around Android Enterprise Device Owner provisioning, Device Policy Manager policy enforcement, kiosk lockdown, remote management, secure APK updates and administrator-authorised privileged actions.}
{Kotlin / MDM}

\projectcard
{\faTv}
{Distributed Android Digital Signage Platform}
{Worked on Kotlin Android-based digital-signage and synchronisation systems focused on REST API integration, content delivery, remote device management, Gradle release packaging, update distribution and offline-first resilience.}
{REST / Gradle}

\projectcard
{\faServer}
{Pairing-Based Domain Onboarding Platform}
{Built a guided onboarding platform for Windows Server and Active Directory environments, covering server/client pairing, DNS configuration, domain-join validation, SMB home-directory setup, Group Policy and Folder Redirection workflows.}
{AD / GPO}

\projectcard
{\faKey}
{Windows SSO / Kerberos to JWT Prototype}
{Designed a working authentication flow where Windows domain login is reused to access protected backend services through Kerberos/SPNEGO validation and RS256 JWT trust.}
{SSO}


\end{document}
